\chapter{Installation}

\begin{warning}
    The OpenChat Zimlet and Extension are already installed in the default Zimbra installation starting from Zimbra 8.8.0.

    Any modification to the package/database may lead to a fail during the Zimbra Upgrade.

    Support for any Zimbra version prior to 8.8.0 is not provided.
\end{warning}

This chapter will guide the administrator through the manual installation of Zimbra OpenChat.

Zimbra OpenChat is designed specifically for Zimbra 8.8.0+, otherwise should be considered at `beta'
stage and you should not install it in a production environment.

\section{Requirements}
    \begin{itemize}
        \item Zimbra 8.8.0+
        \item 25MB of free space on disk
        \item Administrative access on Zimbra
        \item A modern browser (like Firefox 35+ or Google Chrome 45+)
    \end{itemize}

\section{Preliminary setup}

    Get and build the sources as described in the \autoref{sect:buildfromsrcs}.

\subsection{Networking}

    Make sure these ports are opened and exposed for a fully functional OpenChat server:
    \begin{description}
        \item [5269] XMPP Server-to-Server communication. Used between servers on the same cluster.
        \item [5222] XMPP Default server port, see \autoref{sect:confkeys}
        \item [5223] XMPP Default legacy SSL port, see \autoref{sect:confkeys}
    \end{description}

    If the mailbox is into a multi-server installation, make sure the servers can see and connect to each other.

\subsection{Database}

    Zimbra OpenChat Extension uses the Zimbra database to store some informations like:
    \begin{itemize}
        \item Information of the users
        \item Relations between the users (the buddy list information)
        \item Event messages which will be delivered and/or stored in the chat history (if enabled, see \autoref{sect:confkeys})
    \end{itemize}

    To create the database and the tables required by the OpenChat Extension type these commands:
    \begin{verbatim}
# As zimbra
mysql <<\EOF
  CREATE DATABASE `chat`
    DEFAULT CHARACTER SET `utf8`
    DEFAULT COLLATE `utf8_general_ci`;
  GRANT ALL PRIVILEGES ON chat.* TO zimbra;
  USE chat;
  CREATE TABLE `USER` (
    `ID` int(11) NOT NULL AUTO_INCREMENT,
    `ADDRESS` varchar(256) NOT NULL,
    PRIMARY KEY (`ID`)
  );
  CREATE TABLE `RELATIONSHIP` (
    `USERID` int(11) NOT NULL,
    `TYPE` tinyint(4) NOT NULL,
    `BUDDYADDRESS` varchar(256) NOT NULL,
    `BUDDYNICKNAME` varchar(128) NOT NULL,
    `GROUP` varchar(256) NOT NULL DEFAULT ''
  );
  CREATE TABLE `EVENTMESSAGE` (
    `ID` int(11) NOT NULL AUTO_INCREMENT,
    `USERID` int(11) NOT NULL,
    `EVENTID` varchar(36) DEFAULT NULL,
    `SENDER` varchar(256) NOT NULL,
    `TIMESTAMP` bigint(20) DEFAULT NULL,
    `MESSAGE` text,
    PRIMARY KEY (`ID`)
  );
EOF
    \end{verbatim}

\section{Installation of the packages}
\label{sect:installpkgs}

    To install the Extension packages copy them into the Zimbra class path. The Zimlet package need to be installed like
    any other Zimlet for Zimbra.

    Copy the Zimbra Extension packages:
    \begin{verbatim}
# As root
mkdir -p /opt/zimbra/lib/ext/openchat
cp /tmp/OpenChat/build/extension/openchat.jar /opt/zimbra/lib/ext/openchat/
cp /tmp/OpenChat/build/extension/zal.jar /opt/zimbra/lib/ext/openchat/
    \end{verbatim}

    Once the packages are in the right place is required a mailbox restart to load the extension:
    \begin{verbatim}
# As zimbra
zmmailboxdctl restart
    \end{verbatim}

    Deploy the Zimlet package:
    \begin{verbatim}
# As zimbra
zmzimletctl deploy /tmp/OpenChat/build/zimlet/com_zextras_chat_open.zip
    \end{verbatim}

    By default the zimlet is enabled for the Zimbra `default' class of service (COS).
    Enable the zimlet on the required COSes from the administration console.
